%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Yahoo} % Organization
    {Taipei, Taiwan} % Location
    {Jan. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrated core business logic from a legacy component to our existing ad search engine to leverage the scalability advantages of our current framework.}
        \item {Mentoring 2 interns to know the workflow of product ads and help them with their summer project. Worked as a course assistant in an agile workshop for Yahoo Taiwan interns.}
        \item {Collaborated with data scientists from Yahoo Israel to apply RoAS bidding model to product ads, providing Yahoo's advertising partners with a new bidding strategy.}
        \item {Designed and led a junior engineer in developing a next-generation search ad system with embedding matching.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer} % Job title
    {} % Organization
    {} % Location
    {Sep. 2019 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Constructed an ETL pipeline for extracting TW market search product ads. Also worked on troubleshooting and maintenance of the pipeline that processes over 150 million data regularly.}
        \item {Collaborated with Yahoo Taiwan data team, improved TW search product ads revenue by 26\% by enabling Chinese product tagging. My main job was to design and code refactor on ad system for applying the new tagger.}
        \item {Improved TW search product ads revenue by 100\% by adding a new feature: diversity of search results. The feature solved the pain point of Yahoo's advertising partners and gave their ads more opportunities to show.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {National Taiwan University} % Organization
    {Taipei, Taiwan} % Location
    {Sep. 2018 - June. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted in hosting an AI competition with over 700 participants. My work included the collection of contest topics and the program to evaluate the precision of submitted answers.}
      \end{cvitems}
    }

%---------------------------------------------------------
% \cventry
%    {Summer Intern} % Job title
%    {Yahoo} % Organization
%    {Taipei, Taiwan} % Location
%    {Jul. 2018 - Aug. 2018} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Developed an action recognition system using deep learning techniques, and applied it on Yahoo video search.}
%      \end{cvitems}
%    }

%---------------------------------------------------------
\end{cventries}
